### 2017-11-21 2017/KAZAN_LJM/paper_lobach.tex
min -> \min + красивые кавычки

\thank{
This research was supported by the Russian Science Foundation, project No 16-11-10150 "Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance"
}
}

@@

A multidimensional global optimization problem can be stated as follows: to find a global minimum point $y^\ast \in R^N$ where the optimized function $\varphi(y)$ has the minimum value, i.e.
\begin{equation}
\varphi^\ast = \varphi(y^\ast) = min \{\varphi(y): y\in D \},
\end{equation}
where $D$ is the search domain with given boundary vectors $a$ and $b$
\[
D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\}.
\]
It is supposed that the objective function $\varphi(y)$ satisfies a Lipschitz condition
\begin{equation}
\vert \varphi(y') - \varphi(y'') \vert \leq L\| y' - y'' \|, \quad y', y'' \in D,
\end{equation}
where $L > 0$ is the Lipschitz constant, and $\|\ast\|$ is the Euclidian norm in the space $R^N$. Satisfying the Lipschitz condition is important as it allows estimating the global minimum on the basis of the finite number of computed values of the optimized function.

@@

\begin{table}
	\caption{Parallel speedup with respect to the execution time for single computational node}
	\label{tab:tab1}
	\center
	\begin{tabular}{|c|c|c|c|}
	\hline 
		Problem class & \parbox[c]{1.6cm}{ \centering p = 8 } & 
		\parbox[c]{1.6cm}{ \centering p = 16 } &
		\parbox[c]{1.6cm}{ \centering p = 32 } \\
	\hline 
		Simple & 25 & 34 & 109 \\
	\hline 
		Hard   & 5  & 9  & 96  \\
	\hline 
	\end{tabular}
\end{table}

@@

\bibitem{Grishagin1}
V~A.~Grishagin, \textit{On convergence conditions for a class of global search algorithms}, Proceedings of the 3-rd All-Union seminar "Numerical methods of nonlinear programming", Kharkov, 82--84, (1979) [In Russian].

>>>>

\thank{
This research was supported by the Russian Science Foundation, project No 16-11-10150 ``Novel efficient methods and software tools for time-consuming decision making problems using supercomputers of superior performance''
}
}

@@

A multidimensional global optimization problem can be stated as follows: to find a global minimum point $y^\ast \in R^N$ where the optimized function $\varphi(y)$ has the minimum value, i.e.
\begin{equation}
\varphi^\ast = \varphi(y^\ast) = \min \{\varphi(y): y\in D \},
\end{equation}
where $D$ is the search domain with given boundary vectors $a$ and $b$
\[
D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\}.
\]
It is supposed that the objective function $\varphi(y)$ satisfies a Lipschitz condition
\begin{equation}
\vert \varphi(y') - \varphi(y'') \vert \leq L\| y' - y'' \|, \quad y', y'' \in D,
\end{equation}
where $L > 0$ is the Lipschitz constant, and $\|\ast\|$ is the Euclidian norm in the space $R^N$. Satisfying the Lipschitz condition is important as it allows estimating the global minimum on the basis of the finite number of computed values of the optimized function.

@@

\begin{table}
	\caption{Parallel speedup with respect to the execution time for single computational node}
	\label{tab:tab2}
	\center
	\begin{tabular}{|c|c|c|c|}
	\hline 
		Problem class & \parbox[c]{1.6cm}{ \centering p = 8 } & 
		\parbox[c]{1.6cm}{ \centering p = 16 } &
		\parbox[c]{1.6cm}{ \centering p = 32 } \\
	\hline 
		Simple & 25 & 34 & 109 \\
	\hline 
		Hard   & 5  & 9  & 96  \\
	\hline 
	\end{tabular}
\end{table}

@@

\bibitem{Grishagin1}
V~A.~Grishagin, \textit{On convergence conditions for a class of global search algorithms}, Proceedings of the 3-rd All-Union seminar ``Numerical methods of nonlinear programming'', Kharkov, 82--84, (1979) [In Russian].
